MSOA domestic Electricity and Gas maps

### 2021-08-26 LSOA Deprevation.Rmd
Adding in notes on how the overlay map works

# plotting the indices of dep 2019 of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = IMDScore)) +
  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
  labs(caption = "Winchester")
```
####Difference from 2015 to 2019
```{r Creating the dfference in IMD score variable}
imd_lsoa_2015 <- readr::read_csv(paste0(dataFolder, "Indices of Multiple Deprivation/Indices_of_Multiple_Deprivation_(IMD)_2015.csv"))
imd_lsoa_2019 <- readr::read_csv(paste0(dataFolder, "Indices of Multiple Deprivation/Indices_of_Multiple_Deprivation_(IMD)_2019.csv"))
imd_lsoa_2015$imd2015 <- imd_lsoa_2015$'Index of Multiple Deprivation (IMD) Score'
imd_lsoa_2019$imd2019 <- imd_lsoa_2019$'IMDScore'

imd_lsoa_2015$LSOA11CD <-imd_lsoa_2015$lsoa11cd
imd_lsoa_2019$LSOA11CD <-imd_lsoa_2019$lsoa11cd

merged_imd <- merge(imd_lsoa_2015, imd_lsoa_2019, by =lsoa11cd, all = TRUE)
names(merged_imd)
merged_imd$imd_diff<-as.numeric(merged_imd$imd2019)-merged_imd$imd2015
summary(merged_imd)
```
```{r Mapping the change in IMD Score}
merged_imd$lsoa11cd <- merged_imd$"lsoa11cd" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_imd20152019 <- merge(lsoa_sf_data, merged_imd) #merging these
names(lsoa_imd20152019)##BROKEN
##ggplot2::ggplot(lsoa_imd20152019) +
 ## geom_sf(aes(fill=mc_diff))+ 
  ##scale_fill_continuous(name="Change in Gas: Mean kWh per meter", low="green",high="red")+
  ##labs(caption ="Solent (all MSOAs)")
```
#####Looking at the cities in more detail
```{r Southampton LSOA Gas}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(merged_imd, LAD11NM == "Southampton")
# plotting the gas consumption of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `imd_diff`)) +
  scale_fill_continuous(name = "Change in IMD score", low = "green", high = "red") +
  labs(caption = "Southampton")
```
```{r Portsmouth LSOA Gas}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(merged_imd, LAD11NM == "Portsmouth")
# plotting the gas consumption of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `imd_diff`)) +
  scale_fill_continuous(name = "Change in IMD score", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Winchester LSOA Gas}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(merged_imd, LAD11NM == "Winchester")
# plotting the gas consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `imd_diff`)) +
  scale_fill_continuous(name = "Change in IMD score", low = "green", high = "red") +
  labs(caption = "Winchester")
```

>>>>

# plotting the indices of dep 2019 of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = IMDScore)) +
  scale_fill_continuous(name = "IMD Score", low = "green", high = "red") +
  labs(caption = "Winchester")
```
####Difference from 2015 to 2019
```{r Creating the dfference in IMD score variable}
imd_lsoa_2015 <- readr::read_csv(paste0(dataFolder, "Indices of Multiple Deprivation/File_5_ID_2015_Scores_for_the_Indices_of_Deprivation.csv")) # see https://www.gov.uk/government/statistics/english-indices-of-deprivation-2015 - this file has the actual indices in it, the other files (I don't know which you are using) have the ranks
imd_lsoa_2019 <- readr::read_csv(paste0(dataFolder, "Indices of Multiple Deprivation/Indices_of_Multiple_Deprivation_(IMD)_2019.csv"))
imd_lsoa_2015$imd2015 <- imd_lsoa_2015$'Index of Multiple Deprivation (IMD) Score'
imd_lsoa_2019$imd2019 <- imd_lsoa_2019$'IMDScore'

#use names(imd_lsoa_2015) to see what the column (variable) names are!
imd_lsoa_2015$LSOA11CD <-imd_lsoa_2015$`LSOA code (2011)` # <- this does!
imd_lsoa_2019$LSOA11CD <-imd_lsoa_2019$lsoa11cd

merged_imd <- merge(imd_lsoa_2015, imd_lsoa_2019, 
                    by = "LSOA11CD", # you have to use the LSOA11CD variable you just created! 'lsoa11cd' doesn't exist in these two datasets...
                    all = TRUE)
names(merged_imd)
merged_imd$imd_diff<-as.numeric(merged_imd$imd2019)-merged_imd$imd2015
summary(merged_imd)
```
```{r Mapping the change in IMD Score}
merged_imd$lsoa11cd <- merged_imd$LSOA11CD #creating a variable with the LSOA code in the same name as in sf_data - check what you created above!
lsoa_imd20152019 <- merge(lsoa_sf_data, merged_imd) #merging these
names(lsoa_imd20152019)## fixed
ggplot2::ggplot(lsoa_imd20152019) +
 geom_sf(aes(fill=imd_diff))+ 
 scale_fill_continuous(name="Change in IMD score", low="green",high="red")+
 labs(caption ="Solent (all LSOAs)")
```
#####Looking at the cities in more detail
```{r Southampton LSOA IMD}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_imd20152019, LADnm == "Southampton") # check names of variables! Use the data file with the geometry in it
# plotting the gas consumption of Southampton in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = imd_diff)) +
  scale_fill_continuous(name = "Change in IMD score", low = "green", high = "red") +
  labs(caption = "Southampton")
```
```{r Portsmouth LSOA IMD}
#Cities such as Portsmouth disappear due to their density, we will now map Portsmouth alone to see this area in more detail
mapData <- dplyr::filter(lsoa_imd20152019, LADnm == "Portsmouth")
# plotting the gas consumption of Portsmouth in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `imd_diff`)) +
  scale_fill_continuous(name = "Change in IMD score", low = "green", high = "red") +
  labs(caption = "Portsmouth")
```
```{r Winchester LSOA Gas}
#Cities such as Winchester disappear due to their density, we will now map Winchester alone to see this area in more detail
mapData <- dplyr::filter(lsoa_imd20152019, LADnm == "Winchester")
# plotting the gas consumption of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = `imd_diff`)) +
  scale_fill_continuous(name = "Change in IMD score", low = "green", high = "red") +
  labs(caption = "Winchester")
```

### 2021-08-26 MSOA domestic Elec and Gas.Rmd
Adding in notes on how the overlay map works

st_coord_sys <- st_crs(msoa_domgas20102019) # check coord system
st_coord_sys$epsg # current coord system ? Leaflet wants EPSG: 4326

@@

qpal <- colorNumeric("Reds", map_df_trans$mc_diff, n = 9)

leaflet(map_df_trans) %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addPolygons(color = ~qpal(mc_diff),
              fillOpacity = 0.6, weight = 1.5, popup = ~(MSOA11CD), # popups clicked
              highlight = highlightOptions(
                weight = 5,
                color = "#666",
                fillOpacity = 0.7,
                bringToFront = TRUE))

>>>>

st_coord_sys <- st_crs(msoa_domgas20102019) # check coord system
st_coord_sys$epsg # current coord system 27700 Leaflet wants EPSG: 4326 so we need to transform

@@

qpal <- colorNumeric("Reds", map_df_trans$mc_diff, n = 9)#This is setting the colour that wil used later?

leaflet(map_df_trans) %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addPolygons(color = ~qpal(mc_diff),
              fillOpacity = 0.6, weight = 1.5, popup = ~(MSOA11CD), # popups clicked

              ##label =~(popup_text),
             ##labelOptions -labelOptions(
               ##style = list("font-weight"= "normal", padding ="2px 2px"),
               ##direction ="auto"),

               highlight = highlightOptions(
                weight = 5,
                color = "#666",
                fillOpacity = 0.7,
                bringToFront = TRUE))
